Handwritten Digit Recognition Using Deep Convolutional Neural Network*

### 2022-04-24 paper/paper.tex
Ran inkscape to generate tex diagrams Added the diagrams to the paper Rhanged the line plots to 2 different plots Retrained the model

\documentclass[conference]{IEEEtran}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{graphicx}

@@

\section{CNNs And Their Applications}
\Blindtext

\section{The MNIST Dataset}
\Blindtext

\section{The Architecture Used}
\Blindtext

\section{Model Evaluation}
\blindtext

@@

%\bibliographystyle{IEEEtran}
%\bibliography{paper.bib}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{import}

@@

\section{CNNs And Their Applications}
\Blindtext
\cite{Goodfellow-et-al-2016}

\section{The MNIST Dataset}
\cite{6296535}
\Blindtext

\section{The Architecture Used}
\begin{figure}[!htp]
    \centering
    \def\svgwidth{\columnwidth}
    \scriptsize
    \import{./figs/}{cnn_architecture.pdf_tex}
\end{figure}
\Blindtext

\section{Model Evaluation}
\begin{figure}[!htp]
    \centering
    \scriptsize
    \subfloat[Training and validation accuracy\label{performance:accuracy}]{
        \def\svgwidth{0.5\columnwidth}
        \import{./figs/}{accuracy.pdf_tex}
    }
    \subfloat[Training and validation loss\label{performance:loss}]{
        \def\svgwidth{0.5\columnwidth}
        \import{./figs/}{loss.pdf_tex}
    }
    \caption{The per--epoch progress of the model's performance }
\end{figure}
\begin{figure}[!htp]
    \centering
    \def\svgwidth{\columnwidth}
    \scriptsize
    \import{./figs/}{confusion_matrix.pdf_tex}
    \caption{Confusion matrix of the trained model}\label{fig:confusion_matrix}
\end{figure}
\blindtext
\begin{figure}[!htp]
    \centering
    \def\svgwidth{\columnwidth}
    \Huge
    \import{./figs/}{bar_plot.pdf_tex}
    \caption{The accuracy of the model at detecting each digit}\label{fig:confusion_matrix_normalized}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{paper.bib}
